Classless Java: Tuning Java Interfaces

### 2015-12-02 paper/sections/Formalization.tex
S3 summary

\section{Interaction of Interface Methods with Interface Composition}
From Java 8 interfaces can have three type of methods: abstract, default, and
static methods.
\begin{itemize}

@@

During our experimentation, we found a bug in ECJ (Eclipse compiler for Java):
the case \textbf{M} extending \textbf{B3} and \textbf{A1} is accepted by
ECJ4.5.1 and rejected by javac.  By email communication with Brian Goetz
(leading Java 8 designer) we have confirmed that the expected behaviour is
rejection, hence this is a bug in ECJ.\footnote{This bug is fixed in the ECJ
  developer brunch , but not released as a stable version yet.}
%Table~\ref{table:javabug} shows the method overriding bug in Java. In the
%example, there are 6 interfaces \texttt{A1,A2,A3,B1,B2,B3} with methods all
%named as \texttt{m} which are either abstract or default methods. If we define a
%new interface \texttt{M} that extends two of these interfaces, then the method
%overriding result is shown in the table. For example, row2 col2 means \texttt{M
%  extends A1,B1}. The result is \texttt{ERROR} because the abstract method
%\texttt{T m();} in \texttt{A1} conflicts with the method \texttt{default T m()
%  {...}} in \texttt{B1}. Readers may also figure out other extending cases by
%following this way of interpretation.

>>>>

\section{Interaction of Interface Methods with Interface Composition}
Before formalizing our annotation, we summarize methods interaction/shadowing 
mechanism in Java 8 interfaces and especially. We show several interesting cases
and summarize compilation result of method composition into 3 categories:
conflict error, accepted (both abstract) and conservative error. Meanwhile we
also show different composition handling mechanism among traits, javac and ECJ.

From Java 8 interfaces can have three type of methods: abstract, default, and
static methods.
\begin{itemize}

@@

During our experimentation, we found a bug in ECJ (Eclipse compiler for Java):
the case \textbf{M} extending \textbf{B3} and \textbf{A1} is accepted by
ECJ4.5.1 and rejected by javac.  By email communication with Brian Goetz
(leading Java 8 designer) we have confirmed that the expected behaviour is
rejection, hence this is a bug in ECJ.\footnote{This bug was also reported by
  others and is fixed in the ECJ developer brunch, but not released as a stable
  version yet.}
%Table~\ref{table:javabug} shows the method overriding bug in Java. In the
%example, there are 6 interfaces \texttt{A1,A2,A3,B1,B2,B3} with methods all
%named as \texttt{m} which are either abstract or default methods. If we define a
%new interface \texttt{M} that extends two of these interfaces, then the method
%overriding result is shown in the table. For example, row2 col2 means \texttt{M
%  extends A1,B1}. The result is \texttt{ERROR} because the abstract method
%\texttt{T m();} in \texttt{A1} conflicts with the method \texttt{default T m()
%  {...}} in \texttt{B1}. Readers may also figure out other extending cases by
%following this way of interpretation.
